---
title: "p8105_hw6_yc4016"
output: github_document
date: "2022-12-01"
author: "Yishan Chen"
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(modelr)
library(mgcv)

set.seed(1)
```



# Problem 1

* To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```
* In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.
* We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```
* As with $r^2$, this distribution is somewhat skewed and has some outliers. 
* The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 


# Problem 2
```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  mutate(city_state = str_c(city, state, sep = ", ", collapse = NULL),
         homicide_situation = as.numeric(disposition == "Closed by arrest")) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")),
         victim_race %in% c("White", "Black")) %>% 
  mutate (victim_age = as.numeric(victim_age),
          homicide_situation = as.numeric(homicide_situation))
  
homicide_df
```


```{r}
fit_logistic_baltimore = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD") %>%
  glm(homicide_situation ~ victim_age + victim_sex + victim_age, data = ., family = binomial()) 

fit_logistic_baltimore
```


```{r}
fit_logistic_baltimore %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         lower_bound = exp(estimate - 1.96 * std.error),
         upper_bound = exp(estimate + 1.96 * std.error)) %>%
  select(term, estimate, OR, lower_bound, upper_bound) %>%
  filter(term == "victim_sexMale") %>% 
  knitr::kable(digits = 3)
```


```{r}
fit_logistic_all =
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(models = map(data, ~glm(homicide_situation ~ victim_age + victim_sex + victim_age, data = .x, family = binomial())),
         results = map(models, broom::tidy)) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  mutate(OR = exp(estimate),
         lower_bound = exp(estimate - 1.96 * std.error),
         upper_bound = exp(estimate + 1.96 * std.error)) %>%
  filter(term == "victim_sexMale") %>% 
  select(city_state, OR, lower_bound, upper_bound)

fit_logistic_all

fit_logistic_all %>% 
    knitr::kable(digits = 3)
```


```{r}
plot = 
  fit_logistic_all %>% 
    mutate(city_state = fct_reorder(city_state, OR)) %>% 
    ggplot(aes(x = city_state, y = OR, color = city_state)) + 
    geom_point() + 
    geom_errorbar(aes(ymin = lower_bound, ymax = upper_bound)) + 
    theme(axis.text.x = element_text(angle=90, hjust = 1)) + 
    labs(x = "City_states",
         y = "Estimated OR",
         title = "Estimated ORs with CIs for all cities for homicides comparing male/female victims") +
         theme(legend.position = "none") 

plot
```




# Problem 3

```{r}
birthweight = 
  read_csv("data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(babysex = as.factor(babysex),
          frace = as.factor(frace),
          malform = as.factor(malform), 
          mrace = as.factor(mrace)) %>% 
  drop_na()

birthweight
```
* No missing data

```{r}
model_fit = lm(bwt ~ babysex + bhead + bwt + delwt + gaweeks + malform + menarche + mheight + momage + mrace, data = birthweight)

model_fit %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

summary(model_fit)
```
* The model is a linear regression model. It has include variable contains baby's information and basic mother's information (babysex, bhead, bwt, delwt, gaweeks, malform, menarche, mheight, momage, mrace)

```{r}
birthweight = 
  birthweight %>% 
  add_predictions(model_fit) %>% 
  add_residuals(model_fit)

birthweight
```
* I have added the predictions and residuals. 

```{r}
plot1 =
  birthweight %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.5, cex=0.5) +
  labs(title = "Residuals against fitted values",
       x = "Fitted values",
       y = "Residuals") 

plot1
```
* I have create a plot that is residuals against fitted values

```{r}
model1 = lm(bwt ~ blength + gaweeks, data = birthweight)

model1 %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

summary(model1)



model2 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight)

model2 %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

summary(model2)
```
* I have create two models.

```{r, warning = FALSE}
cv_df = 
  crossv_mc(birthweight, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble)) %>% 
  mutate(model1 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = birthweight)),
         model2 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + bhead*babysex + bhead*blength*babysex, data = birthweight)),
         model_fit = map(.x = train, ~lm(bwt ~ babysex + bhead + bwt + delwt + gaweeks + malform + menarche + mheight + momage + mrace, data = birthweight))) %>% 
  mutate(rmse_model1 = map2_dbl(.x = model1, .y = test, ~rmse(.x,.y)),
         rmse_model2 = map2_dbl(.x = model2, .y = test, ~rmse(.x,.y)),
         rmse_model_fit = map2_dbl(model_fit, .y = test, ~rmse(model = .x, .y))) 

cv_df 
```
* I have create model comparison between model1, model1 and model_fit using cross validation.

```{r}
plot2 =
  cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(everything(),
               names_to = "model", 
               values_to = "rmse",
               names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()

plot2
```
* From plot2, model2 has lowest rmse, so model2 might be the best model.
